---
name: George
surname: Oduor
position: "Data Analyst | Statistical Modeling | Financial Industry Expertise"
address: "P.O.Box 21,Ugunja 46006"
phone: +254711894704
www: georgeoduor.com
email: "george.wamaya@gmail.com"
github: georgeoduor
linkedin: georgeoduor
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

Results-driven Data Analyst with a proven track record in quantitative and qualitative data analysis. Specializing in statistical modeling, credit analytics, and financial industry knowledge. Proficient in Python, R, and advanced Excel for data-related projects. Experienced in SQL and database management. Possesses strong leadership, effective communication, and teamwork abilities. Seeking a challenging role as a Business Analyst at Lipa Later to utilize analytical skills in driving performance and process improvements.

# SKILLS

-   **Data Analysis**: Proficient in Python and R programming for data analysis and visualization. Skilled in using R Shiny, ggplot2, plotly, and Python Dash for data visualization.

-   **Database Management**: Hands-on proficiency in relational databases like MySQL and PostgreSQL.

-   **Credit Analytics**: Extensive experience in credit analysis, credit risk assessment, and MOBILE loan underwriting.

-   **Statistical Modeling**: Strong knowledge of statistical modeling techniques, including regression analysis, time series analysis, and hypothesis testing.

-   **Financial Industry Knowledge**: Familiarity with lending and credit best practices, regulatory requirements, and trends in credit analytics.

-   **Project Management:** Experienced in stakeholder management and successful project delivery, coordinating cross-functional teams to meet tight timelines.

-   **Communication and Leadership**: Strong leadership skills with a focus on collaboration and teamwork.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Bsc Statistics & Programming", "2011-2017", "Kenyatta University", "Nairobi, Kenya",
  "Certificate in Leadership Development", "2017", "Kenyatta University", "Nairobi, Kenya",
  "Kenya Certificate of Secondary Education", "2007 - 2010", "Sawagongo High School", "Siaya, Kenya"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# EXPERIENCE

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  2019 , "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```

# Publications

```{r}
library(dplyr)
knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```
